\documentclass{article}
\usepackage[utf8]{inputenc}

\usepackage{fullpage}	% for the margins
\usepackage{mathpazo}	% for the Palatino font (optional) 
\usepackage{multirow}   % For multirow table cells

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                      %
% .  This is the voluntary template for the assignments in TDT4242.    % 
%               Remember to fix TODOs before submitting.               %
%                  Changing the template is allowed.                   %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{\textsc{ \normalsize Norwegian University of Science and Technology\\
TDT4242 Advanced Software Engineering, spring 2020}\\[0.5cm]
\LARGE \textbf{Exercise 2}\\
\large \textbf{Group Number: NN}\\% TODO: edit group number
\textbf{Peer Group Number: NN}% TODO: edit group number
} 
\author{Ola Nordmann \and Kari Nordmann} % TODO: edit your names 

\begin{document}
\maketitle

\section{Introduction}
\begin{itemize}
    \item Summarize shortly what they have done
\end{itemize}


\section{Implementation of the new features by using DevOps environment}
\begin{itemize}
    \item Write about the used DevOps tool.
    \item Describe the new features which you are going to implement.
    \item Explain the design and implementation of new features.
    \item Write about the way of using the DevOps environment to implement the new features.
    \item Write about meeting with your peer group and their feedback (You should also list the participants of each meeting of your group and your peer group.)
\end{itemize}


\section{Automated test scripts to get full statement coverage}
\begin{itemize}
    \item Summarize the statement coverage results.
    \item Provide information about where to find the test scripts in your code for running these tests.
\end{itemize}


\section{Automated test scripts for black-box testing}
\begin{itemize}
    \item Summarize the test results
    \item Provide information about where to find the test scripts in your code for running these tests.
\end{itemize}


\section{Acceptance tests}
\begin{itemize}
    \item Acceptance test cases and results. The test case template is below
\end{itemize}


\begin{table}[]
    \centering
    \begin{tabular}{|p{7cm}|p{8cm}|}
        \hline
        Test Case Name & Correct PIN entry on first try \\ \hline
        Test Case ID & TC-1 \\ \hline
        Description & A customer enters the PIN number correctly on the first attempt \\ \hline
        \multirow{3}{*}{Preconditions needed to run this test case} & 1. The expected PIN is "2468" \\ \cline{2-2} 
                                                                    & 2. Screen 2 is displayed \\ \hline
        \multicolumn{2}{|c|}{\textit{Event Sequence}} \\ \hline
        \textit{Input events (performed by tester)} & \textit{Output events (observed by system tester)} \\ \hline
        & 1. Screen 2 shows '- - - -' \\ \hline
        2. Touch digit 2 & \\ \hline
        & 3. Screen 2 shows '- - - *' \\ \hline
        4. Customer touches digit 4 & \\ \hline
        & 5. Screen 2 shows '- - * *' \\ \hline
    \end{tabular}
    \caption{Test Case 1 - Correct PIN entry on first try}
    \label{tab:test_case_1}
\end{table}


\end{document}